%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass[margin, centered]{res}
\topmargin=-0.5in
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.5in
\itemsep=0in
\parsep=0in
\newsectionwidth{1in}
\usepackage[pdftex]{graphicx}
\usepackage{etaremune}
\usepackage{enumitem}
\usepackage{wrapfig}
\usepackage[dvipsnames]{xcolor}
\usepackage{helvet}
\usepackage{comment}

\usepackage[colorlinks = true,
            linkcolor = BrickRed,
            urlcolor  = BrickRed,
            citecolor = BrickRed,
            anchorcolor = BrickRed]{hyperref}
\setlength{\textwidth}{6.5in} % Text width of the document
\setlength{\textheight}{720pt}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------\
\begin{center}
    \hspace{-\hoffset}
    \huge {\textcolor{black}{\textbf{Sourav Majumder}}}
\end{center}

\vspace{-5mm}
\moveleft\hoffset\vbox{\hrule width 19cm height 0.5pt}
\vspace{-8mm}
%\textbullet~ \href{http://adivijaykumar.github.io}{Website}
\begin{center}
    \hspace{-\hoffset}
    \href{mailto:sourav@iisc.ac.in}{sourav@iisc.ac.in} ~\textbullet~ \ Indian Institute of Science, Bengaluru,  India.
\end{center}
\vspace{-7mm}
\begin{resume}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Reserach Interests}
Quantum hybrid devices, Superconducting qubits
\\
\section{Education}
\textbf{\href{https://www.iisc.ac.in/}{Indian Institute of Science (IISc), Bengaluru}}\\
\textbf{Graduate Student in Physics} \hfill 2017 - \textit{Present}

\textbf{\href{https://www.iisc.ac.in/}{Indian Institute of Science (IISc), Bengaluru}}\\
\textbf{M.S. Physics} \hfill 2015 - 2017

\textbf{\href{https://rkmrc.in/}{Ramakrishna Mission Residential College (RKMRC), Narendrapur}}\\
\textbf{B.Sc. (Hons.) Physics} \hfill 2012 - 2015

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Employment}
\textbf{Graduate Student}
\\
\textbf{\href{https://www.iisc.ac.in/}{Indian Institute of Science (IISc), Bengaluru}}\\
\emph{Mentored by \href{https://sites.google.com/view/sqd-lab}{Dr. Vibhor Singh}} \hfill Aug 2017 - \textit{Present}\\
\textit{Topic - Hybrid quantum devices}

\textbf{Summer Project Intern}
\\
\textbf{\href{https://www.iisc.ac.in/}{Indian Institute of Science (IISc), Bengaluru}}\\
\emph{Mentored by \href{https://sites.google.com/view/sqd-lab}{Dr. Vibhor Singh}} \hfill May 2017 - July 2017\\
\textit{Topic - Transmon in 3D Cavity}


\section{Publications}
\begin{etaremune}
	\item 
	\textbf{Optomechanical Platform with a Three-dimensional Waveguide Cavity}\\
	Bindu Gunupudi, Soumya Ranjan Das, Rohit Navarathna, Sudhir Kumar Sahu, \textbf{Sourav Majumder}, and Vibhor Singh\\
	\textit{Phys. Rev. Applied} 11, 024067 - Published 26 February 2019, \href{https://arxiv.org/abs/1902.06215}{arXiv:1902.06215}. 
	
	\item 
	\textbf{Large flux-mediated coupling in hybrid electromechanical system with a transmon qubit}\\
	Tanmoy Bera, \textbf{Sourav Majumder}, Sudhir Kumar Sahu, and Vibhor Singh\\
	\textit{Communications Physics} 4, 12 (2021) - Published 19 January 2021, \href{https://arxiv.org/abs/2001.05700}{arXiv:2001.05700}. 
	
\end{etaremune}


\section{Conferences, and other Meetings}
\begin{itemize}[leftmargin=*]
	\item Talk titled \textit{Relaxation of a transmon qubit from unconfined states and resurgence of coherence} at \textbf{APS March Meeting 2021}, 
	American Physical Society, March 2021.
	\item	Participant, \textbf{International Workshop on Electron and Ions in/on Helium (EIH 2020)}, IISc, Bengaluru, India, January 2020.
	\item Poster titled \textit{Losses and dynamic range of a strongly driven circuit-QED system} at \textbf{ISNTT-2019}, 
	NTT Basic Research Laboratory, Atsugi, Japan, November 2019.
	\item Poster titled \textit{Towards the development of a hybrid system for synthesizing single phonon state} at \textbf{In-house Symposium}, 
	IISc, Bengaluru, India, November 2018.
	\item Poster titled \textit{Fabrication and characterization of a superconducting 3D-transmon qubit} at \textbf{In-house Symposium}, 
	IISc, Bengaluru, India, November 2017.
\end{itemize}
\section{Hackathons}
\begin{itemize}[leftmargin=*]
	\item Participant, \textbf{The Qiskit Challenge India},  Qiskit, September 2018

\end{itemize}



%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Technical \hspace{2mm} Skills}
\textbf{Programming Languages} - Python, C, C++, Shell Script\\
\textbf{Softwares} - MATLAB, Mathematica \\
\textbf{Tools/Frameworks} - \LaTeX, Git



\section{Scores and Awards}
\begin{itemize}[leftmargin=*]
 \item Scored 960/990 on the \href{https://www.ets.org/gre/subject/about/content/physics}{Subject GRE in Physics}, October 2017
 \item Secured all-India rank 21 in the \href{https://www.jest.org.in/}{Joint Entrance Screening Test (JEST)}, 2018 for admission into Physics PhD programmes in India
 \item Awarded the \href{https://www.icts.res.in/academic/summer-research-program}{ICTS S.N. Bhatt Memorial Excellence Fellowship}, 2018
 \item Selected for the \href{http://web-japps.ias.ac.in:8080/fellowship2018/}{Summer Research Fellowship} of the Indian Academy of Sciences in 2016
 \item Recepient of the \href{http://www.inspire-dst.gov.in/scholarship.html}{INSPIRE-DST Scholarship for Higher Education} for the period 2013 to 2018
\end{itemize}

\section{References}
\begin{itemize}[leftmargin=*]
 \item Prof. Parameswaran Ajith, ICTS -- \href{mailto:ajith@icts.res.in}{ajith@icts.res.in}
 \item Dr. Shasvath Kapadia, ICTS -- \href{mailto:shasvath.kapadia@icts.res.in}{shasvath.kapadia@icts.res.in}
 \item Dr. Sumit Kumar, AEI Hannover -- \href{mailto:sumit.kumar@aei.mpg.de}{sumit.kumar@aei.mpg.de}
 \item Prof. Bala Iyer, ICTS -- \href{mailto:bala.iyer@icts.res.in}{bala.iyer@icts.res.in}
\end{itemize}

\end{resume}
\end{document}
